Analysis

### 2022-05-25 EDA_SCREEN.Rmd
save to BED

```{r libraries}
library(tidyverse)
library(readxl)
library(writexl)
library(GenomicRanges)
```

@@

# Input files
# Human CTCF-bound cCRE (hg38)
fileNameIn1 <- file.path(dir_data, "data/GRCh38-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/GRCh38-CTCF.bed", fileNameIn1)
# Mouse CTCF-bound cCRE (mm10)
fileNameIn2 <- file.path(dir_data, "data/mm10-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/mm10-CTCF.bed", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg38.SCREEN.GRCh38_CTCF.RData")
fileNameOut2 <- file.path(dir_data, "results/mm10.SCREEN.mm10_CTCF.RData")
```

@@

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg38.SCREEN.GRCh38_CTCF, file = fileNameOut1)
save(list = mm10.SCREEN.mm10_CTCF, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
```

>>>>

```{r libraries}
library(tidyverse)
library(readxl)
library(writexl)
library(GenomicRanges)
library(rtracklayer)
```

@@

# Input files
# Human CTCF-bound cCRE (hg38)
fileNameIn1 <- file.path(dir_data, "data/GRCh38-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/GRCh38-CTCF.bed", fileNameIn1)
# Mouse CTCF-bound cCRE (mm10)
fileNameIn2 <- file.path(dir_data, "data/mm10-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/mm10-CTCF.bed", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg38.SCREEN.GRCh38_CTCF.RData")
fileNameOut1.1 <- file.path(dir_data, "results/hg38.SCREEN.GRCh38_CTCF.bed")
fileNameOut2 <- file.path(dir_data, "results/mm10.SCREEN.mm10_CTCF.RData")
fileNameOut2.1 <- file.path(dir_data, "results/mm10.SCREEN.mm10_CTCF.bed")
```

@@

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg38.SCREEN.GRCh38_CTCF, file = fileNameOut1)
save(list = mm10.SCREEN.mm10_CTCF, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg38.SCREEN.GRCh38_CTCF, fileNameOut1.1)
export.bed(mm10.SCREEN.mm10_CTCF, fileNameOut2.1)
```
